**Density Dependence**

### 2023-02-13 Rmd/ddMac.Rmd
m1 corrected

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.2/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))
```

>>>>

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.15/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))
```

### 2023-02-13 Rmd/ddWhb.Rmd
m1 corrected

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.2/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.1,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))
```

>>>>

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.2/(150^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.1,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))
```
